---
title: "Student Performance Report"
subtitle: "AAST Classroom Emotion System"
author: "Generated by AI Analytics"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    latex_engine: xelatex
params:
  student_id: "231006131"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(lubridate)

# Load data (assuming relative paths from shiny-app directory)
emotions <- read.csv("../../python-api/data/exports/emotions.csv", stringsAsFactors = FALSE)
student_data <- emotions %>% filter(student_id == params$student_id)
student_name <- if(nrow(student_data) > 0) student_data$name[1] else "Unknown Student"
```

# Executive Summary: `r student_name` (`r params$student_id`)

This report provides a detailed analysis of the student's emotional engagement and cognitive load across recent lectures. The "Confidence Rate" reflects the student's overall focus and positive engagement levels.

## Key Metrics

```{r metrics}
if(nrow(student_data) > 0) {
  avg_conf <- mean(student_data$engagement_score, na.rm = TRUE)
  top_emotion <- names(sort(table(student_data$emotion), decreasing = TRUE))[1]
  
  cat(paste0("- **Average Confidence Rate:** ", round(avg_conf * 100, 1), "%\n"))
  cat(paste0("- **Primary Emotional State:** ", top_emotion, "\n"))
} else {
  cat("No data available for this student.")
}
```

## Confidence Rate Trend

The chart below illustrates the student's confidence rate over time. High values indicate strong focus and engagement.

```{r trend, fig.height=4}
if(nrow(student_data) > 0) {
  ggplot(student_data, aes(x = as.POSIXct(timestamp), y = engagement_score)) +
    geom_line(color = "#002147", size = 1) +
    geom_point(color = "#C9A84C") +
    theme_minimal() +
    labs(x = "Time", y = "Confidence Rate") +
    ylim(0, 1)
}
```

## Emotion Distribution

Breakdown of emotional states captured during lectures.

```{r emotions, fig.height=4}
if(nrow(student_data) > 0) {
  emotion_counts <- student_data %>%
    group_by(emotion) %>%
    summarise(count = n()) %>%
    mutate(pct = count / sum(count))
  
  ggplot(emotion_counts, aes(x = emotion, y = pct, fill = emotion)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c(
      "Focused" = "#1B5E20", "Engaged" = "#4CAF50", "Confused" = "#FFC107",
      "Frustrated" = "#FF9800", "Anxious" = "#9C27B0", "Disengaged" = "#F44336"
    )) +
    theme_minimal() +
    labs(x = "Emotion", y = "Percentage") +
    theme(legend.position = "none")
}
```

## Cognitive Load Analysis

Cognitive load is calculated based on periods of confusion and frustration. Sustained high load may indicate a need for additional support.

```{r load, fig.height=4}
if(nrow(student_data) > 0) {
  load_data <- student_data %>%
    mutate(time_bucket = floor_date(as.POSIXct(timestamp), "5 minutes")) %>%
    group_by(time_bucket) %>%
    summarise(cognitive_load = mean(emotion %in% c("Confused", "Frustrated"), na.rm = TRUE))
  
  ggplot(load_data, aes(x = time_bucket, y = cognitive_load)) +
    geom_line(color = "orange") +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
    theme_minimal() +
    labs(x = "Time", y = "Cognitive Load") +
    ylim(0, 1)
}
```

## AI Intervention Plan

Based on the observed patterns, the following interventions are recommended:

```{r ai_plan, results='asis'}
# In a real scenario, we'd fetch this from the database/API
# For the report, we'll provide a placeholder or fetch if possible
cat("1. **Targeted Review:** Focus on concepts covered during peak confusion periods.\n")
cat("2. **Engagement Boost:** Encourage participation in group discussions to reduce disengagement.\n")
cat("3. **Stress Management:** Monitor anxiety levels during high-stakes assessments.\n")
```

---
*Confidential Report - AAST Classroom Emotion System*
